The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd
Generalise column-creation in ngrams function

emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof")))

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017]. We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling. In LDA, each document is a mixture of topics and each topic is a mixture of words. The probability of a term being part of a topic is given by the beta statistic. The probability of a document being part of a topic is given by the gamma statistic.

@@

# Fit LDA model
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

@@

# The top n words that are the most common in each topic
emu_theses_top_terms <- get_top_words_per_topic(emu_theses_topics, 20)

emu_theses_top_terms |> 
  ggplot(aes(reorder(term, beta), beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3)
```

```{r}
# Which are the top n most frequently used words in all theses?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 20)
```

@@

## TO DO: generalise bigrams and trigrams into ngrams function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  separate(bigram, into = c("first", "second"), sep = " ", remove = FALSE) |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word")) |> 
  filter(str_detect(first, "[a-z]") & 
         str_detect(second, "[a-z]"))

>>>>

emu_theses$text_clean <- emu_theses$text_clean |>
  str_remove_all(find_meta_stopwords(emu_theses)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof")))

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

@@

# We will use the Latent Dirichlet Allocation (LDA) algorithm for topic modeling
# In LDA, each document is a mixture of topics and each topic is a mixture of words
emu_theses_lda <- LDA(emu_theses_dtm, k = 2, control = list(seed = 2023))
emu_theses_lda

@@

# The top 10 words that are the most common in each topic
emu_theses_top_terms <- emu_theses_topics |> 
  group_by(topic) |> 
  top_n(20, beta) |> 
  ungroup() |> 
  arrange(topic, -beta)

emu_theses_top_terms |> 
  mutate(term = reorder(term, beta)) |> 
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, 
                           top_n = 3, 
                           title_col = "title", 
                           word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 5, 
                         word_col = "word")
```

```{r}
# Which are the top n most frequently used words in all theses`?
emu_theses_top_20 <- get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 20, 
                         word_col = "word")
```

@@

## Add lemmas as optional column to ngram function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

spacyr::spacy_parse(emu_theses_bigrams$first)
